SAT Competition 2020\tnoteref{title}

### 2021-06-05 paper/main.tex
disqulified solvers and further stats

To participate in the Main track, solvers needed to output certificates for both the satisfiable and the unsatisfiable instances. Moreover, the source code of the solver were required 
to be made publicly available. 
Solvers not complying with either of these two criteria were only evaluated in a so-called No-Limits track and were not eligible for the Main track awards.
The No-Limits track thus enabled participation of closed-source solvers (not being able or willing to expose the source code for legal or other reasons) 
as well as portfolio solvers (combining two or more core SAT solvers developed by different groups of authors; c.f.~Sect.~\ref{sec:rules}).
However, solvers in No-Limits still competed against all other solvers submitted to the Main Track.
Thus, to deserve a mention, a No-Limits solver would need rank among the best-performing solvers among the Main Track participants.
The No-Limits track was only evaluated with respect  \emph{newly} submitted benchmark instances, i.e., on instances
which were submitted to SAT Competition 2020.

@@

@@

@@

@@

New this year was the Cloud track, dedicated to evaluating distributed solvers running on multiple machines in a network. 
%\textcolor{red}{Not sure if terms ``distributed'' vs ``parallel'' are clear, could be more explicitly explained?}. 
%Similar to the Parallel track, the solvers ran on the Amazon cloud, but using 100 machines of the type m4.4xlarge, which have 16 virtual cores and 64GB of memory. 
Communication between the machines is possible using MPI and SSH.
%The wall-clock timeout is 1000 seconds and the same benchmarks were used as in the Main and Parallel track. \textcolor{red}{repetitive? also mentioned below?}

@@

>>>>

To participate in the Main track, solvers needed to output certificates for both the satisfiable and the unsatisfiable instances. 
Moreover, the source code of the solver were required to be made publicly available. 
Solvers not complying with either of these two criteria were only evaluated in a so-called No-Limits track and were not eligible for the Main track awards.
The No-Limits track thus enabled participation of closed-source solvers (not being able or willing to expose the source code for legal or other reasons) 
as well as portfolio solvers (combining two or more core SAT solvers developed by different groups of authors; c.f.~Sect.~\ref{sec:rules}).
Without limit, submissions could be solvers that use a lookup table or similar to determine solutions. 
Thus, the No-Limits track was only evaluated with respect to \emph{newly} submitted benchmark instances, i.e., on instances which were submitted to SAT Competition~2020.

However, solvers in No-Limits still competed against all other solvers submitted to the Main Track.
Thus, to deserve a mention, a No-Limits solver would need rank among the best-performing solvers among the Main Track participants.
The top ranked solvers in the No-Limits track were the same as in the Main track. 
This also indicates the stability of results under the exclusion of old benchmark instances.

@@

We evaluated all 64 submitted solver configurations of which eight have been explicitly submitted to the No-Limits track, and four configurations were demoted to the No-Limits track due to wrong certificates. 
A total of six configurations got disqualified due to wrong answers. 
This left us with 46 configurations of 22 solvers inluding one Glucose hack.

@@

In this competition, two of the six submissions got disqualified, such that we had only four solvers competing in the Incremental track.

@@

In the Parallel track, we evaluated ten solvers (in 14 configurations) out of which three solvers got disqualified due to wrong answers.

@@

New this year was the Cloud track, dedicated to evaluating distributed solvers running on multiple machines in a network. 
%\textcolor{red}{Not sure if terms ``distributed'' vs ``parallel'' are clear, could be more explicitly explained?}. 
%Similar to the Parallel track, the solvers ran on the Amazon cloud, but using 100 machines of the type m4.4xlarge, which have 16 virtual cores and 64GB of memory. 
Communication between the machines is possible using MPI and SSH.
%The wall-clock timeout is 1000 seconds and the same benchmarks were used as in the Main and Parallel track. \textcolor{red}{repetitive? also mentioned below?}
We evaluated six solvers in this track.

@@

The first instantiation of an Application track has been a Planning track. 
The results show that different solvers take the lead when we only evaluate for a single application. 
We intend to run further instantiations of the Application track. 
In the next competition, we will compile a set of 200 cryptographic benchmark instances for a Crypto track.
